---
title: "My Paper"
author: "My Name"
abstract: "This is the abstract."
journal: "Journal xyz"
date: "01-01-2020"
output: 
  pdf_document:
  keep_tex: TRUE
numbersections: TRUE
link-citations: true
bibliography: references.bib
csl: journal-of-banking-and-finance.csl
header-includes:
  \usepackage{float} 
  \usepackage{hyperref} 
            \hypersetup{colorlinks=true,linkcolor=blue, urlcolor=green}
  \AtBeginDocument{
  \hypersetup{pdfborder={0 0 1},linkbordercolor=red, urlbordercolor=red}}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(kableExtra)
```

# Introduction

This **paper** is *about* abc.
\newline
This \textbf{paper} is \textit{about} \textcolor{red} {abc}.


This paper is divided into four further sections.
The next [section](#literaturereview) provides a brief review of
relevant literature.

\hyperref[fig:figure_1]{Figure~\ref*{fig:figure_1}} displays the relationship between disp and mpg.

\hyperref[tab:table_1]{Table~\ref*{tab:table_1}} shows the first rows of the mtcars dataset.


\newpage
 
# Literature review {#literaturereview}

[@konigsteinWhyFirmsShould2001]

@konigsteinFairnessOneprincipaltwoagentsGame2003

# Study design

## Data

The average HP (horse Power) of all cars is `r mean(mtcars$hp)`.


```{r chunk1, echo=T, include=T}
mean(mtcars$hp)
```

## Methodology

# Empirical Results

## Sample A

```{r figure_1, echo=FALSE, fig.cap= "relationship disp and mpg", fig.align="center", out.width = "50%"}
mtcars%>%
  ggplot(aes(x=disp,y=mpg))+
  geom_point()+
  geom_smooth(method = "lm",se = F)
```

### Sample A-1

```{r table_1, echo=FALSE}
mtcars%>%
  head(5)%>%
  kable(booktabs = T,caption="Table mtcars")%>%
  kable_styling(
    latex_options = c( "hold_position"),
    position = "center",
    full_width = F)
```

### Sample A-2

## Sample B

# Conclusion

# References {-}

<div id="refs"></div>