---
title: "My Paper"
author: "My Name"
abstract: "This is the abstract."
date: "01-01-2020"
output: 
  pdf_document:
  keep_tex: TRUE
numbersections: TRUE
link-citations: TRUE
header-includes:
  \usepackage{float} 
  \usepackage{hyperref} 
  \hypersetup{colorlinks=true,linkcolor=blue}
  \AtBeginDocument{\hypersetup{pdfborder={0 0 1}, linkbordercolor=red}}
---

```{r packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(kableExtra)
```


# Introduction


This paper is divided into four further sections.
The next [section](#literaturereview) provides a brief review of
relevant literature.

The [section 3](#studydesign)

# Literature review {#literaturereview}

Markdown code

normal text –> normal text
**bold** –> bold
*italics* –> italics

LaTex code

\textbf{text} –>text
\textit{text} –>text
\underline{text} –>text––––
\textcolor{red}{text} –>text
\newline –>linebreak
\newpage –>newpage

# Study design {#studydesign}

## Data

The average HP (horse Power) of all cars is `r mean(mtcars$hp)`.

```{r chunk1, include=T, echo=T}
mean(mtcars$hp)
```

## Methodology


# Empirical Results

## Sample A

```{r figure1, echo=FALSE, message=FALSE, fig.cap="Relationship disp and mpg", out.height="10%"}
mtcars%>%
  ggplot(aes(x=disp,y=mpg))+
  geom_point()+
  geom_smooth(method = "lm",se = F)
```




### Sample A-1


```{r}
mtcars%>%
  head(5)%>%
  kable(booktabs = T, caption="Table mtcars")%>%
  kable_styling(
    latex_options = c("hold_position"),
    position = "center",
    full_width = T)
```



### Sample A-2

## Sample B

# Conclusion