---
title: "My Paper"
author: "My Name"
abstract: "This is the abstract."
date: "01-01-2020"
output: 
  pdf_document:
    keep_tex: TRUE
numbersections: True
link-citations: TRUE
header-includes:
  \usepackage{float} 
  \usepackage{hyperref} 
            \hypersetup{colorlinks=true,linkcolor=blue}
  \AtBeginDocument{
  \hypersetup{pdfborder={0 0 1},linkbordercolor=red}}
---

```{r options, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
```


# Introduction

This **paper** is *about* abc.
\newline
\underline{This} \textbf{paper} is \textit{about} \textcolor{red}{abc}.

This paper is divided into four further sections.
The next [section](#literaturereview) provides a brief review of
relevant literature.
The [section 3](#studydesign)

\newpage

# Literature review {#literaturereview}

# Study design {#studydesign}

## Data

The average HP (horse Power) of all cars is `r mean(mtcars$hp)`.

```{r chunk1, eval=FALSE, echo=FALSE, include=TRUE}
mean(mtcars$hp)
```

```{r}
source("script1.R")
```


```{r figure_1, echo=FALSE, message=FALSE, fig.cap="Relationship disp and mpg", out.height = "70%"}
mtcars%>%
  ggplot(aes(x=disp,y=mpg))+
  geom_point()+
  geom_smooth(method = "lm",se = F)
```


```{r table_1}
mtcars%>%
  head(5)%>%
  kable(booktabs = T, caption="Table mtcars")%>%
  kable_styling(
    latex_options = c("hold_position"),
    position = "center",
    full_width = F)
```


## Methodology

# Empirical Results

## Sample A

### Sample A-1

### Sample A-2

## Sample B

# Conclusion

# References {-}