---
title: "Creating Scientific Articles with R Markdown"
author: Tobias Kellner
date: '`r Sys.setlocale(locale = "English") ; format(Sys.time(), "%B %d, %Y")`'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
```

## Programs

- MiKTex for Windows, MacTeX for Mac, TeX Live for Linux, ("tinytex")
- Zotero
- Zotero-Addon in Firefox

## Package requirements

packages: rticles, tidyverse, citr, knitr, kableExtra

```r 
install.packages(
c("rticles","tidyverse","knitr","kableExtra","devtools")
)

devtools::install_github("crsh/citr")
```

```r 
library(tidyverse)
library(knitr)
library(kableExtra)
library(rticles)
```

## Why R Markdown?

> - Text and code in one document
> - Consistency (several reports in same format, templates)
> - Reproducibility
> - Easy to switch output between PDF, Word, and HTML (and many other formats)
> - One R Markdown file for your whole project (data import, cleaning, mergeing, manipulation, calculations,...)
> - Large number of extension packages and a big community of R users

## YAML header

YAML: Yet Another Markup Language

What It Is: YAML is a human friendly data serialization standard for programming languages.

Used for configuration files

Example:

```
---
title: "My Paper"
author: "My Name"
abstract: "This is the abstract."
journal: "Journal xyz"
date: "01-01-2020"
output: pdf_document
---
```


<style>
pre {
    line-height: 1.2em;
    font-size: 20px;
}
</style>

## Headers and sections

```r
# Introduction

# Literature review

# Study design

## Data

## Methodology

# Empirical Results

## Sample A

### Sample A-1

### Sample A-2

## Sample B

# Conclusion
```

## Text

- Markdown code
<br/>
`normal text`   --> normal text
<br/>
`**bold**`    --> **bold**
<br/>
`*italics*`   --> *italics*

- LaTex code
<br/>
`\textbf{text}`     -->$\textbf{text}$
<br/>
`\textit{text}`    -->$\textit{text}$
<br/>
`\underline{text}`    -->$\underline{text}$
<br/>
`\color{red}{text}`   -->$\color {red} {text}$
<br/>
`\newline`    -->linebreak
<br/>
`\newpage`    -->newpage

## Hyperlinks I

- Hyperlinks to sections
```
---
link-citations: true
header-includes:
  \usepackage{hyperref} 
            \hypersetup{colorlinks=true,linkcolor=blue}
  \AtBeginDocument{
  \hypersetup{pdfborder={0 0 1},linkbordercolor=orange}}
---

# Introduction

This paper is divided into four further sections.
The next [section](#literaturereview) provides a brief review of
relevant literature.

\newpage

# Literature review {#literaturereview}
```

## Embed code

- Inline code

````
The average HP (horse Power) of all cars is `#r mean(mtcars$hp)`.
````
The average HP (horse Power) of all cars is `r mean(mtcars$hp)`

- Code chunks

````{
```
{r chunk1, include=T, echo=T}

mean(mtcars$hp)
```
````

```{r chunk1, include=T, echo=F}
mean(mtcars$hp)
```

## Chunk options
```{
eval=TRUE,
include=TRUE,
echo=TRUE,
error=TRUE,
message=TRUE,
warning=TRUE,
```

## Figures
```{r figure_1, fig.cap="Relationship between disp and mpg", out.width = "70%", message=FALSE, echo=TRUE}
mtcars%>%
  ggplot(aes(x=disp,y=mpg))+
  geom_point()+
  geom_smooth(method = "lm",se = F)
```

## Figures II

- Chunk options

````{
```
{r chunk_name, message=FALSE, echo=TRUE, 
fig.cap= "figure caption",
fig.align="center",
fig.height=5,
fig.width=7,
out.height = "70%",
out.width = "70%"
}
```
````

## Tables
```{
mtcars%>%
  head(5)%>%
  kable(format = "latex", booktabs = T)%>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    position = "center",
    full_width = T)
```
Literature:
https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf

## Hyperlinks II

- Chunk label must be named!

- Hyperlinks to figures

`\hyperref[fig:figure_1]{Figure~\ref*{fig:figure_1}}`

- Hyperlinks to tables

`\hyperref[tab:table_1]{Table~\ref*{tab:table_1}}`


## Collect literature with Zotero

- Create new bibliography file in Zotero

- Collect literature with Zotero Connector(Firefox Addon)

- Export Zotero bibliography in the working directory

## Insert citations

```{
---
bibliography: references.bib
biblio-style: "apalike"
---
```
- bibliography styles:
https://www.bibtex.com/bibliography-styles/

- Start the `CITR`-Addin

## Hyperlinks III

### Hyperlinks to citations:
```
---
header-includes:
  \usepackage{hyperref}
    \hypersetup{urlcolor=green}
  
  \AtBeginDocument{
    \hypersetup{urlbordercolor=red}
  }
---
```

- see more:

https://de.wikibooks.org/wiki/LaTeX-W%C3%B6rterbuch:_hyperref


## Templates

- Creating submission-ready documents

- Package `rticles` provides templates for various journals and publishers, for example:
  - Elsevier journal submissions
  - Springer journal submissions

- Choose `rticles`-templates in the settings of a new markdown document


## Outlook and further Information

Visual editor in RStudio 1.4:

- https://rstudio.com/products/rstudio/download/preview/

Literature:

- https://bookdown.org/yihui/rmarkdown/

- https://rmarkdown.rstudio.com/