---
title: "How to reporting results with R Markdown"
author: "Wasilios Hariskos and Tobias Kellner"
date: "25 11 2020"
output: pdf_document
header-includes:
    - \usepackage{dcolumn}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)

# Data science packages
library(tidyverse) 
# leveneTest
library(car)
```

# The independent t-test

```{r data, echo=FALSE}
# Generate factor levels
Group <- gl(n = 2, 
            k = 12, 
            labels = c("Picture", "Real Spider"))

# Enter anxiety scores
Anxiety <- c(30, 35, 45, 40, 50, 35, 55, 25, 30, 45, 40, 50,
             40, 35, 50, 55, 65, 55, 50, 35, 30, 50, 60, 39)

# Create data frame
spider <- tibble(picture = Anxiety[Group == "Picture"],
                 real = Anxiety[Group == "Real Spider"])
# Print data
spider
```

12 arachnophobes were exposed to a picture of a spider and 12 different arachnophobes were exposed to a real spider. Their anxiety was measure in each condition. Andy Field et al. report the results of an independent t-test as follows (page 385): 

"On average, participants experienced greater anxiety from real spiders (M = 47.00, SE = 3.18), than from pictures of spiders (M = 40.00, SE = 2.68). The difference was not significant t(21.39) = -1.68, p > .05; however, it did represent a medium sized effect r = .34."

We will recreate their results and report them with R Markdown. The data is saved as `spider`and you access the two columns with `spider$picture`and `spider$real`.

We can use the function `mean(x)` to compute the means but we have to write our own function `se(x)` to compute the stanard error of the mean, i.e., the standard deviation of the sampling distribution.

```{r function se}
se <- function(x) {
  N <- length(x)
  sd(x)/sqrt(N)
  }
```

We get the following result:

On average, participants experienced greater anxiety from real spiders (M = `r mean(spider$real)`, SE = `r se(spider$real)`), than from pictures of spiders (M = `r mean(spider$picture)`, SE = `r se(spider$picture)`).

We can use `round(x, 2)` to improve the output:

On average, participants experienced greater anxiety from real spiders (M = `r mean(spider$real)`, SE = `r round(se(spider$real), 2)`), than from pictures of spiders (M = `r mean(spider$picture)`, SE = `r round(se(spider$picture), 2)`).

Next, we have to conduct a t-test to see whether the difference in group means is statistically significant.

```{r ttest}
ttest <- t.test(x = spider$real,
                y = spider$picture)
ttest
```

We want to write "The difference was not significant t(21.39) = -1.68, p > .05". We get the degrees of freedom for the t-statistic with `ttest$parameter`, the value of the t-statistic with `ttest$statistic` and the p-value for the test with `ttest$p.value`.

The difference was not significant t(`r ttest$parameter`) = `r ttest$statistic`, p = `r ttest$p.value`.

We can use `options()` to improve the output (the default is 7).

```{r}
options(digits = 2)
```

The difference was not significant t(`r ttest$parameter`) = `r ttest$statistic`, p = `r ttest$p.value`.

Last we want to report the effect size: "however, it did represent a medium sized effect r = .34." To do this we write a small function:

```{r}
reffect <- function(myttest){
  df = myttest$parameter
  t = myttest$statistic
  r = sqrt(t^2 / (t^2 + df))
  as.numeric(r)
}
```

We get: however, it did represent a medium sized effect r = `r reffect(myttest = ttest)`. Putting everything together, we obtain the final result:

On average, participants experienced greater anxiety from real spiders (M = `r mean(spider$real)`, SE = `r se(spider$real)`), than from pictures of spiders (M = `r mean(spider$picture)`, SE = `r se(spider$picture)`). The difference was not significant t(`r ttest$parameter`) = `r ttest$statistic`, p = `r ttest$p.value`; however, it did represent a medium sized effect r = `r reffect(myttest = ttest)`.

\newpage
# Multiple lm() models using apsrtable

```{r}
m1 <- lm(Fertility ~ Education , data = swiss)
m2 <- lm(Fertility ~ Education + Agriculture, data = swiss)
m3 <- lm(Fertility ~ . , data = swiss)
```

```{r, message=FALSE, warning=FALSE, results='asis'}
# install.packages("apsrtable")
apsrtable::apsrtable(m1, m2, m3, Sweave = TRUE)
```

\newpage
# Multiple lm() models using stargazer

```{r results='asis'}
# install.packages("stargazer")
# If output: html_document
# stargazer::stargazer(m1, m2, m3, type = "html")
# If output: pdf_document
stargazer::stargazer(m1, m2, m3)
```





