---
title: "My Paper"
author: "My Name"
abstract: "This is the abstract."
journal: "Journal xyz"
date: "01-01-2020"
output:
  pdf_document: 
    keep_tex:  true
bibliography: references.bib
csl: journal-of-banking-and-finance.csl
numbersections: TRUE
link-citations: true
header-includes:
  \usepackage{float}
  \usepackage{hyperref} 
            \hypersetup{
            colorlinks=true,
            linkcolor=blue,
            urlcolor=blue}
  \AtBeginDocument{
  \hypersetup{pdfborder={ 0 0 1},linkbordercolor=red,
  urlbordercolor=red}}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
```

# Introduction


This **paper** is *about* abc.
\newline
This \textbf{paper} \underline{is} \textit{about} \textcolor {red} {abc}.

This paper is divided into four further sections.
The next [section](#literaturereview) provides a brief review of
relevant literature.

\hyperref[fig:figure_1]{Figure~\ref*{fig:figure_1}}

\hyperref[tab:table_1]{Table~\ref*{tab:table_1}}



\newpage

# Literature review {#literaturereview}

[@konigsteinWhyFirmsShould2001]


@konigsteinFairnessOneprincipaltwoagentsGame2003

# Study design

The average HP (horse Power) of all cars is `r mean(mtcars$hp)`

```{r chunk1, echo=TRUE}

mean(mtcars$hp)
```

## Data

## Methodology

# Empirical Results

```{r figure_1, echo=FALSE,fig.cap= "relationship disp and mpg", fig.align="center", out.width = "50%"}
mtcars %>%
  ggplot(aes(x = disp, y = mpg)) +
  geom_point(aes(color = factor(cyl))) +
  geom_smooth(method = "lm", se = F)
```

## Sample A

```{r table_1, echo=FALSE}
mtcars%>%
  head(5)%>%
  kable(booktabs = T,caption="Table mtcars")%>%
  kable_styling(
    latex_options = c( "hold_position"),
    position = "center",
    full_width = F)
```

### Sample A-1

### Sample A-2

## Sample B

# Conclusion

# References {-}

<div id="refs"></div>


\newpage

# Appendix {-}


